The Hot Hand Fallacy in Call of Duty Search and Destroy

### 2022-08-25 paper/paper.Rmd
longtable -> table, other small notation fixes

---
title: "The Hot Hand Fallacy in Call of Duty"
authors:
  - name: Tony ElHabr
    email: anthonyelhabr@gmail.com
    url: https://tonyelhabr.rbind.io
  - name: Andrew ElHabr
    email: andrewelhabr@gatech.edu
    affiliation: Georgia Institute of Technology
    department: School of Industrial and Systems Engineering (ISyE)
    location: Atlanta, Georgia, USA
abstract: |
  Our research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD). First, we find evidence suppOrting the hypothesis that round win probability can be modeled as a constant across rounds in the series, although not at the naive 50%. Second, we examine post-streak round win probability, given the series outcome. Given streak length, series length, and series winner, we find no evidence that post-streak win rate is significantly different than expected, suggesting that the perception of momentum at the team level is deceiving. Wald-Wolfowitz run tests also fail to provide evidence for the hot hand phenomenon.
bibliography: references.bib
keywords:
  - esports
  - Call of Duty
  - hot hand
  - runs test
output:
  rticles::arxiv_article:
    includes:
      in_header: preamble.tex
---

@@

6-0 sweeps make up 4.7% of all series, while 6-5 series make up 23.7% of series. The observed offensive round win percentage across all rounds is $\tau_O$ = 47.8%.[^10] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e. the number of round wins by each team prior to an upcoming round). Offensive round win rate is not quite constant, although never veers more than 10% from $\tau_O$.

@@

```{=tex}
\begin{longtable}{crrrrrr}
\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins. Numbers in parentheses are sample sizes.}\label{tbl:cod-o-win-prop-by-series-state} \\
\toprule
& \multicolumn{6}{c}{Offense round wins} \\ 
\cmidrule(lr){2-7}
Defense round wins & 0 & 1 & 2 & 3 & 4 & 5 \\ 
\midrule
0 & 47.8\%
(852) & 46.6\%
(408) & 43.1\%
(216) & 43.5\%
(115) & 43.3\%
(67) & 40.5\%
(37) \\ 
1 & 48.6\%
(444) & 49.3\%
(418) & 51.5\%
(309) & 43.4\%
(205) & 43.3\%
(120) & 39.4\%
(99) \\ 
2 & 52.8\%
(218) & 48.9\%
(305) & 48.9\%
(315) & 46.6\%
(262) & 48.7\%
(189) & 42.1\%
(133) \\ 
3 & 54.5\%
(123) & 46.0\%
(200) & 49.6\%
(250) & 45.6\%
(248) & 44.4\%
(214) & 44.8\%
(174) \\ 
4 & 56.9\%
(65) & 54.5\%
(145) & 47.2\%
(193) & 44.7\%
(228) & 55.2\%
(221) & 50.5\%
(208) \\ 
5 & 47.4\%
(38) & 49.4\%
(83) & 47.1\%
(136) & 50.9\%
(175) & 45.2\%
(177) & 46.0\%
(202) \\ 
\bottomrule
\end{longtable}
```
At tournaments, higher-seeded ("better") teams choose whether they want to start on offense in the SnD series played as the second or fifth map, and their opponent is assigned to start on offense in the SnD map not chosen.[^11][^12] Outside of tournaments, teams all play each other twice throughout the season, constituting qualifiers. Each team gets to play the higher-seeded role once in their head-to-head matchups with a given team, despite their win-loss records. Overall, we can argue that potential bias due to stronger teams playing defense---or, if offense, if offense happens to be generally advantageous for a given map---is very minimal.

@@

```{=tex}
\begin{equation}\label{eq:chi-squ}
\chi^2 = \sum^{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)},
\end{equation}
```
in which $R = [6, 7, 8, 9, 10, 11]$ for CoD SnD.

@@

Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected series lasting $r$ rounds, the expected proportion of series given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, and the observed proportions, $\Phi(r)$.

```{=tex}
\begin{longtable}{rrrr}
\caption{The expected proportion of CoD SnD series lasting $r$ rounds, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$. Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum^{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}\label{tbl:cod-prob-series-lasting-r-rounds} \\
\toprule
$r$ & $N(r)$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ \\ 
\midrule
6 & 40 & $4.7\%$ & $3.1\%$ \\ 
7 & 101 & $11.9\%$ & $9.4\%$ \\ 
8 & 141 & $16.5\%$ & $16.4\%$ \\ 
9 & 185 & $21.7\%$ & $21.9\%$ \\ 
10 & 183 & $21.5\%$ & $24.6\%$ \\ 
11 & 202 & $23.7\%$ & $24.6\%$ \\ 
\bottomrule
\end{longtable}
```
```{r}
#| label: cod_series_outcomes_naive_chi
generate_chi_label <- function(statistic, p.value) {
  sprintf('%.1f (%s)', statistic, ifelse(p.value <= 0.01, '<=0.01', as.character(round(p.value, 2))))
}

@@

```{=tex}
\begin{longtable}{lrr}
\caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}\label{tbl:mosteller-methods-results} \\
\toprule
Method & $\phi$ & $\chi^2$ ($p$-value) \\
\midrule
0. Naive & 0.5000 & 16.0 ($\leq$ 0.01) \\
1. Method of moments & 0.5725 & 3.6 (0.6) \\
2. Maximum likelihood & 0.5750 & 3.5 (0.62) \\
3. Minimum ($\chi^2$) & 0.5775 & 3.5 (0.62) \\
\bottomrule
\end{longtable}
```
Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^21] We observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$. $\hat{\Phi}_2(r)$ is also closer to the observed $\Phi(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.

@@

```{=tex}
\begin{longtable}{rrrr}
\caption{The observed proportion of CoD SnD series, $\Phi(r)$, ending in $r$ rounds, compared to the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ and the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$, for constant round win probability.}\label{tbl:expected-series-lengths-alternative-ps} \\
\toprule()
$r$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ = 0.5 & $\hat{\Phi}_2(r)$ = 0.575 \\
\midrule()
\endhead
6 & 4.7\% & 3.1\% & 4.2\% \\
7 & 11.9\% & 9.4\% & 11.2\% \\
8 & 16.5\% & 16.4\% & 17.8\% \\
9 & 21.7\% & 21.9\% & 21.8\% \\
10 & 21.5\% & 24.6\% & 23.0\% \\
11 & 23.7\% & 24.6\% & 22.0\% \\
\bottomrule()
\end{longtable}
```
Observing that $\hat{\Phi}_2(r)$ reasonably matches $\Phi(r)$ (especially in comparison to $\hat{\Phi}_0(r)$), along with the null hypothesis rejection shown in Table \ref{tbl:mosteller-methods-results}, we can say that the constant round win probability assumption is valid in CoD SnD series with the appropriate choice of $\phi$ ($\approx 0.575$).

@@

Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.[^22] Table \ref{tbl:cod-pw3r-pl3r} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win rate, $P^{+|kr}$, following streaks of $k=3$ round wins given the series outcome.

@@

```{=tex}
\begin{longtable}{rcrrrrr}
\caption{Given the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r}$, and proportion of round wins, $P^{+|k=3,r}$, among $N^{k=3,r}$ instances where a team could win after the streak ($P^{+|k=3,r} = \frac{r^{+|k=3,r}}{N^{k=3,r}}$). Additionally, the notional and MS expected proportions, $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$ respectively.}
\label{tbl:cod-pw3r-pl3r} \\

\toprule
$r$ & \text{Win series?} & $r^{+|k=3,r}$ & $N^{k=3,r}$ & $P^{+|k=3,r}$ & $\hat{P}^{+|k=3,r}_0$ & $\hat{P}^{+|=k=3,r}_{MS}$ \\ 
\midrule

@@

\bottomrule
\end{longtable}
```
With the exception of $\hat{P}^{+|k,r}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins, all un-adjusted binomial test $p$-values are greater than the $\alpha = 0.05$ confidence level, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion. However, after adjusting the $p$-values with the Benjamini and Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^23]

@@

Now let us explicitly consider the round, $i$. As shown in Table \ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|k,r,i}_0$, is statistically different than the observed $P^{+|k,r,i}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^25] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.

@@

```{=tex}
\begin{longtable}{rrcrrrr}
\caption{Given the round win streak $k=3$, the index of the round immediately following the streak $i$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ instances where a team could win after the streak. Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$. Table restricted to $r \in [10, 11]$, $i < r$, and $N^{k=3,r,i} \geq 10$ for brevity.}
\label{tbl:cod-pw3ri-pl3ri} \\
\toprule
$r$ & $i$ & \text{Win series?} & $r^{+|k=3,r,i}$ & $N^{k=3,r,i}$ & $P^{+|k=3,r,i}$ & $\hat{P}^{+|k=3,r,i}_0$\\ 
\midrule

@@

\bottomrule
\end{longtable}
```
```{r}
#| label: cod_round_arrangements
library(randtests)
simulate_cod_round_arrangements <- function(p = 0.5, n_sims = 10000, seed = 42) {
  n_rounds_max <- 11
  set.seed(seed)
  w <- sample(c(0, 1), size = n_rounds_max * n_sims, replace = TRUE, prob = c(1 - p, p))
  m <- matrix(w, nrow = n_sims, ncol = n_rounds_max)
  # data.frame(x)
  df <- as_tibble(m)
  names(df) <- sprintf('%d', 1:n_rounds_max)
  df$i <- 1:nrow(df)

@@

In Table \ref{tbl:cod-runs}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial success $\phi = 0.575$,[^26] at a confidence level of $\alpha = 0.05$, for $r \in [8, 9, 10]$. In addition to the 13 sequences shown, there are 12 additional sequences for $r = 11$.

@@

```{=tex}
\begin{longtable}{rlrrrr}

\caption{Sequences ($\zeta(r)$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively. The observed count, $N^{\zeta r}$, and proportion, $P^{\zeta r}$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta r}$, and proportion, $\hat{P}^{\zeta r}$. $\hat{N}^{\zeta r}$ is scaled to the observed number of series played, hence its non-integer value.}
\label{tbl:cod-runs} \\

\toprule
r & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
\midrule
8 & - - + + + + + + & 4 & 0.47\% & 7.67 & 0.90\% \\ 
9 & - - - + + + + + + & 4 & 0.47\% & 3.75 & 0.44\% \\ 
10 & + + + + - - - - + + & 1 & 0.12\% & 2.39 & 0.28\% \\ 
10 & + - - - - + + + + + & 0 & 0.00\% & 2.04 & 0.24\% \\ 
10 & + - + - + + - + - + & 3 & 0.35\% & 2.04 & 0.24\% \\ 
10 & + + + - - - - + + + & 2 & 0.23\% & 2.04 & 0.24\% \\ 
10 & - - - - + + + + + + & 2 & 0.23\% & 1.79 & 0.21\% \\ 
10 & + - + - + - + + - + & 3 & 0.35\% & 1.70 & 0.20\% \\ 
10 & + - + + - + - + - + & 0 & 0.00\% & 1.70 & 0.20\% \\ 
10 & + + - - - - + + + + & 1 & 0.12\% & 1.19 & 0.14\% \\ 
10 & + - + - + - + - + + & 3 & 0.35\% & 1.11 & 0.13\% \\ 
10 & + + - + - + - + - + & 0 & 0.00\% & 1.11 & 0.13\% \\ 
10 & + + + + + - - - - + & 2 & 0.23\% & 1.02 & 0.12\% \\ 
\bottomrule
\end{longtable}
```
The relative frequency of the expected proportions are based on 10,000 simulations using the constant round probability $\phi_2 = 0.575$. A test for the difference between the observed and expected proportions of all sequences, $P^{\zeta r}$ and $\hat{P}^{\zeta r}$ respectively, indicates that the null hypothesis---that the two proportions are equal---cannot be rejected for any of the 25 significant sequences.

@@

For the sake of brevity, we did not delve into win rates and streaks split by offensive or defensive role. For example, it would be interesting to look at whether the round win rate is higher after a streaks of three round wins when the team starts the streak as the offensive team. This would mean that, in the round immediately following the latest streak win, the streaking team would be playing defense, where teams are slightly more likely to win on average. On the other hand, streaks of three starting with an offensive round win---theoretically, knowing that $\tau_O$ = 47.7%, the expected frequency is $\tau_O^2 (1 - \tau_O) \approx$ 11.9%---are likely to occur less frequently than such streaks starting with a defensive win---$\tau_O (1 - \tau_O)^2 \approx$ 13.0%---so we would want to account for sample size differences.

>>>>

---
title: "The Hot Hand Fallacy in Call of Duty Search and Destroy"
authors:
  - name: Tony ElHabr
    email: anthonyelhabr@gmail.com
    url: https://tonyelhabr.rbind.io
  - name: Andrew ElHabr
    email: andrewelhabr@gatech.edu
    affiliation: Georgia Institute of Technology
    department: School of Industrial and Systems Engineering (ISyE)
    location: Atlanta, Georgia, USA
abstract: |
  Our research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD). First, we find evidence suppOrting the hypothesis that round win probability can be modeled as a constant across rounds in the series, although not at the naive 50%. Second, we examine post-streak round win probability, given the series outcome. Given streak length, series length, and series winner, we find no evidence that post-streak win rate is significantly different than expected, suggesting that the perception of momentum at the team level is deceiving. Wald-Wolfowitz run tests also fail to provide evidence for the hot hand phenomenon.
bibliography: references.bib
keywords:
  - esports
  - Call of Duty
  - hot hand
  - runs test
output:
  rticles::arxiv_article:
    includes:
      in_header: preamble.tex
---

@@

6-0 sweeps make up 4.7% of all series, while 6-5 series make up 23.7% of series. The observed offensive round win percentage across all rounds is $\bar{\tau}_O$ = 47.8%.[^10] Table \ref{tbl:o-win-prop-by-series-state} shows round win percentages by series "state" (i.e. the number of round wins by each team prior to an upcoming round). Offensive round win rate is not quite constant, although never veers more than 10% from $\bar{\tau}_O$.

@@

```{=tex}
\begin{table}

\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins. Numbers in parentheses are sample sizes.}

\centering
\begin{tabular}{crrrrrr}
\toprule
& \multicolumn{6}{c}{Offense round wins} \\ 
\cmidrule(lr){2-7}
Defense round wins & 0 & 1 & 2 & 3 & 4 & 5 \\ 
\midrule

0 & 47.8\%(852) & 46.6\%(408) & 43.1\%(216) & 43.5\%(115) & 43.3\%(67)  & 40.5\%(37)  \\
1 & 48.6\%(444) & 49.3\%(418) & 51.5\%(309) & 43.4\%(205) & 43.3\%(120) & 39.4\%(99)  \\
2 & 52.8\%(218) & 48.9\%(305) & 48.9\%(315) & 46.6\%(262) & 48.7\%(189) & 42.1\%(133) \\
3 & 54.5\%(123) & 46.0\%(200) & 49.6\%(250) & 45.6\%(248) & 44.4\%(214) & 44.8\%(174) \\
4 & 56.9\%(65)  & 54.5\%(145) & 47.2\%(193) & 44.7\%(228) & 55.2\%(221) & 50.5\%(208) \\
5 & 47.4\%(38)  & 49.4\%(83)  & 47.1\%(136) & 50.9\%(175) & 45.2\%(177) & 46.0\%(202) \\

\bottomrule
\end{tabular}

\label{tbl:o-win-prop-by-series-state}

\end{table}
```
At tournaments, higher-seeded ("better") teams choose whether they want to start on offense in the SnD series played as the second or fifth map, and their opponent is assigned to start on offense in the SnD map not chosen.[^11][^12] Outside of tournaments, teams all play each other twice throughout the season, constituting qualifiers. Each team gets to play the higher-seeded role once in their head-to-head matchups with a given team, despite their win-loss records. Overall, we can argue that potential bias due to stronger teams playing defense---or, if offense, if offense happens to be generally advantageous for a given map---is very minimal.

@@

```{=tex}
\begin{equation}\label{eq:chi-squ}
\chi^2 = \sum_{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)},
\end{equation}
```
in which $R = [6, 7, 8, 9, 10, 11]$ for CoD SnD.

@@

Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected series lasting $r$ rounds, the expected proportion of series given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, and the observed proportions, $\Phi(r)$.

```{=tex}
\begin{table}
\caption{The expected proportion of CoD SnD series lasting $r$ rounds, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$. Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum_{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}

\centering
\begin{tabular}{rrrr}
\toprule
$r$ & $N(r)$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ \\ 
\midrule

6 & 40 & $4.7\%$ & $3.1\%$ \\ 
7 & 101 & $11.9\%$ & $9.4\%$ \\ 
8 & 141 & $16.5\%$ & $16.4\%$ \\ 
9 & 185 & $21.7\%$ & $21.9\%$ \\ 
10 & 183 & $21.5\%$ & $24.6\%$ \\ 
11 & 202 & $23.7\%$ & $24.6\%$ \\

\bottomrule
\end{tabular}

\label{tbl:prob-series-lasts-r-rounds}

\end{table}
```
```{r}
#| label: cod_series_outcomes_naive_chi
generate_chi_label <- function(statistic, p.value) {
  sprintf('%.1f (%s)', statistic, ifelse(p.value <= 0.01, '<=0.01', as.character(round(p.value, 2))))
}

@@

```{=tex}
\begin{table}

\caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}

\centering
\begin{tabular}{lrr}
\toprule
Method & $\phi$ & $\chi^2$ ($p$-value) \\
\midrule

0. Naive & 0.5000 & 16.0 ($\leq$ 0.01) \\
1. Method of moments & 0.5725 & 3.6 (0.6) \\
2. Maximum likelihood & 0.5750 & 3.5 (0.62) \\
3. Minimum ($\chi^2$) & 0.5775 & 3.5 (0.62) \\

\bottomrule
\end{tabular}

\label{tbl:mosteller-methods-results}

\end{table}
```
Table \ref{tbl:alternative-constant-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^21] We observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$. $\hat{\Phi}_2(r)$ is also closer to the observed $\Phi(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.

@@

```{=tex}
\begin{table}
\caption{The observed proportion of CoD SnD series, $\Phi(r)$, ending in $r$ rounds, compared to the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ and the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$, for constant round win probability.}

\centering
\begin{tabular}{rrrrrr}
\toprule
$r$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ = 0.5 & $\hat{\Phi}_2(r)$ = 0.575 \\
\midrule

6 & 4.7\% & 3.1\% & 4.2\% \\
7 & 11.9\% & 9.4\% & 11.2\% \\
8 & 16.5\% & 16.4\% & 17.8\% \\
9 & 21.7\% & 21.9\% & 21.8\% \\
10 & 21.5\% & 24.6\% & 23.0\% \\
11 & 23.7\% & 24.6\% & 22.0\% \\

\bottomrule
\end{tabular}

\label{tbl:alternative-constant-ps}

\end{table}
```
Observing that $\hat{\Phi}_2(r)$ reasonably matches $\Phi(r)$ (especially in comparison to $\hat{\Phi}_0(r)$), along with the null hypothesis rejection shown in Table \ref{tbl:mosteller-methods-results}, we can say that the constant round win probability assumption is valid in CoD SnD series with the appropriate choice of $\phi$ ($\approx 0.575$).

@@

Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.[^22] Table \ref{tbl:pwkr} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win rate, $P^{+|kr}$, following streaks of $k=3$ round wins given the series outcome.

@@

```{=tex}
\begin{table}

\caption{Given the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r}$, and proportion of round wins, $P^{+|k=3,r}$, among $N^{k=3,r}$ instances where a team could win after the streak ($P^{+|k=3,r} = \frac{r^{+|k=3,r}}{N^{k=3,r}}$). Additionally, the notional and MS expected proportions, $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$ respectively.}

\centering
\begin{tabular}{rcrrrrr}
\toprule
$r$ & \text{Win series?} & $r^{+|k=3,r}$ & $N^{k=3,r}$ & $P^{+|k=3,r}$ & $\hat{P}^{+|k=3,r}_0$ & $\hat{P}^{+|=k=3,r}_{MS}$ \\ 
\midrule

@@

\bottomrule
\end{tabular}

\label{tbl:pwkr}

\end{table}
```
With the exception of $\hat{P}^{+|k,r}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins, all un-adjusted binomial test $p$-values are greater than the $\alpha = 0.05$ confidence level, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion. However, after adjusting the $p$-values with the Benjamini and Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^23]

@@

Now let us explicitly consider the round, $i$. As shown in Table \ref{tbl:pw3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|k,r,i}_0$, is statistically different than the observed $P^{+|k,r,i}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^25] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.

@@

```{=tex}
\begin{table}

\caption{Given the round win streak $k=3$, the index of the round immediately following the streak $i$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ instances where a team could win after the streak. Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$. Table restricted to $r \in [10, 11]$, $i < r$, and $N^{k=3,r,i} \geq 10$ for brevity.}

\centering
\begin{tabular}{rrcrrrr}
\toprule
$r$ & $i$ & \text{Win series?} & $r^{+|k=3,r,i}$ & $N^{k=3,r,i}$ & $P^{+|k=3,r,i}$ & $\hat{P}^{+|k=3,r,i}_0$\\ 
\midrule

@@

\bottomrule
\end{tabular}

\label{tbl:pw3ri}

\end{table}
```
```{r}
#| label: cod_round_arrangements
library(randtests)
simulate_cod_round_arrangements <- function(p = 0.5, n_sims = 10000, seed = 42) {
  n_rounds_max <- 11
  set.seed(seed)
  w <- sample(c(0, 1), size = n_rounds_max * n_sims, replace = TRUE, prob = c(1 - p, p))
  m <- matrix(w, nrow = n_sims, ncol = n_rounds_max)
  # data.frame(x)
  df <- as_tibble(m)
  names(df) <- sprintf('%d', 1:n_rounds_max)
  df$i <- 1:nrow(df)

@@

In Table \ref{tbl:ww-sequences}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial success $\phi = 0.575$,[^26] at a confidence level of $\alpha = 0.05$, for $r \in [8, 9, 10]$. In addition to the 13 sequences shown, there are 12 additional sequences for $r = 11$.

@@

```{=tex}
\begin{table}

\caption{Sequences ($\zeta(r)$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively. The observed count, $N^{\zeta r}$, and proportion, $P^{\zeta r}$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta r}$, and proportion, $\hat{P}^{\zeta r}$. $\hat{N}^{\zeta r}$ is scaled to the observed number of series played, hence its non-integer value.}

\centering
\begin{tabular}{rlrrrr}
\toprule
$r$ & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
\midrule
8 & - - + + + + + + & 4 & 0.47\% & 7.67 & 0.90\% \\ 
9 & - - - + + + + + + & 4 & 0.47\% & 3.75 & 0.44\% \\ 
10 & + + + + - - - - + + & 1 & 0.12\% & 2.39 & 0.28\% \\ 
10 & + - - - - + + + + + & 0 & 0.00\% & 2.04 & 0.24\% \\ 
10 & + - + - + + - + - + & 3 & 0.35\% & 2.04 & 0.24\% \\ 
10 & + + + - - - - + + + & 2 & 0.23\% & 2.04 & 0.24\% \\ 
10 & - - - - + + + + + + & 2 & 0.23\% & 1.79 & 0.21\% \\ 
10 & + - + - + - + + - + & 3 & 0.35\% & 1.70 & 0.20\% \\ 
10 & + - + + - + - + - + & 0 & 0.00\% & 1.70 & 0.20\% \\ 
10 & + + - - - - + + + + & 1 & 0.12\% & 1.19 & 0.14\% \\ 
10 & + - + - + - + - + + & 3 & 0.35\% & 1.11 & 0.13\% \\ 
10 & + + - + - + - + - + & 0 & 0.00\% & 1.11 & 0.13\% \\ 
10 & + + + + + - - - - + & 2 & 0.23\% & 1.02 & 0.12\% \\

\bottomrule
\end{tabular}

\label{tbl:ww-sequences}
\end{table}
```
The relative frequency of the expected proportions are based on 10,000 simulations using the constant round probability $\phi_2 = 0.575$. A test for the difference between the observed and expected proportions of all sequences, $P^{\zeta r}$ and $\hat{P}^{\zeta r}$ respectively, indicates that the null hypothesis---that the two proportions are equal---cannot be rejected for any of the 25 significant sequences.

@@

For the sake of brevity, we did not delve into win rates and streaks split by offensive or defensive role. For example, it would be interesting to look at whether the round win rate is higher after a streaks of three round wins when the team starts the streak as the offensive team. This would mean that, in the round immediately following the latest streak win, the streaking team would be playing defense, where teams are slightly more likely to win on average. On the other hand, streaks of three starting with an offensive round win---theoretically, knowing that $\bar{\tau}_O$ = 47.7%, the expected frequency is $\bar{\tau}_O^2 (1 - \bar{\tau}_O) \approx$ 11.9%---are likely to occur less frequently than such streaks starting with a defensive win---$\bar{\tau}_O (1 - \bar{\tau}_O)^2 \approx$ 13.0%---so we would want to account for sample size differences.
